\section{Review of iterative solution techniques applied to the $S_n$
transport equation}
In this section, we first give the multigroup $S_n$ transport equations. Next,
the Source Iteration technique is recalled and the $S_n$ equations are
recast to be solved by a Krylov solver. Previous work on angular
multigrid methods applied as preconditioner to SI is presented. Finally, we
conclude this section with the derivation of the new method.  
\subsection{Multigroup $S_n$ equations} 
Charged particles transport can be described by the Boltzmann equation
\cite{graal} which discretized in energy using the standard multigroup method
\cite{reuss} and in angle using the discrete ordinate method \cite{reuss}, is
given by :
\begin{equation}
\bo_d \cdot \bn \Psi_d^g(\br) + \Sigma_{t,g}^g(\br) \Psi_d^g(\br) = \sum_{g'=0}^G
\sum_{l=0}^L\sum_{m=-l}^l \frac{2l+1}{4\pi}\Sigma_{s,l}^{g'\rightarrow
g}\Phi_{l,m}^{g'}(\br)Y_l^m(\bo_d) + Q_d^g(\br)
\label{discretized}
\end{equation}
where $\br$ is the position in domain $\mathcal{D}$, $E$ is the energy,
$\bo_d=(\mu_d,\varphi_d)$, $\mu_d$ is the cosine of the directional polar angle,
$\varphi_d$ is the directional azimuthal angle, 
$\Psi_d^g(\br)=\int_{E^{g}}^{E^{g-1}}\Psi(\br,\bo_d,E)\ dE$, $\Psi$ is
the angular flux, $Q_d^g(\br) = \int_{E^g}^{E^{g-1}}Q(\br,\bo_d,E) dE$, $Q$ is
a volumetric source, $\Sigma_{t}^g(\br)$ is the multigroup total 
macroscopic cross section, $\Sigma_{s,l}$ is the Legendre moment of 
degree $l$ of $\Sigma_s$ and $\Phi_{l,m}(\br,E)= \int_{4\pi}\Psi(\br,\bo,E)Y_l^{m,*}(\bo)\ d\bo
\approx \sum_{d=1} w_d \Psi(\br,\bo_d,E)Y_l^{m,*}(\bo_d)$ where $Y_l^m$ 
are the spherical harmonics.
Standard boundary conditions can be applied to (\ref{discretized}); the most
commonly employed is the incoming flux boundary condition :
\begin{equation}
\Psi(\br,\bo,E) = g(\br,\bo,E)\textrm{ for }\bo\cdot\bs{n}<0\textrm{ and
}\br\in \partial \mathcal{D},
\label{boundary}
\end{equation} 
where $\partial \mathcal{D}$ is the boundary of the domain $\mathcal{D}$. If $g=0$, equation
(\ref{boundary}) yields vacuum boundary conditions.\\
This equation still needs to be discretized in space but the method proposed
in this paper is not restricted to a particular spatial discretization. For
the results presented here, we use bilinear discontinuous finite elements in
two dimensional space problem \cite{dgfem}.\\ 
Equation (\ref{discretized}) can be written using operator notation as :
\begin{equation}
L \bs{\Psi} = M\Sigma D \bs{\Psi} + \bs{Q}
\label{operator}
\end{equation}
where $\bs{\Psi}$ is a vector containing all the $\Psi_d$, $\bs{Q}$ is a
vector containing all the $Q_d$, $\Sigma$ is a diagonal matrix with the
element $\Sigma_{s,l}$ as diagonal elements, $M$ is the moment-to-discrete
matrix $(\bs{\Psi} = M\bs{\Phi})$, $D$ is the discrete-to-moments matrix
$(\Phi=D\Psi)$ (the moment entries are dictated  by the dimensionality of the
problem) and $L = \bo\cdot + \Sigma_t$ is the streaming + total interaction operator,
inverted direction by direction (transport sweeps). The inversion can be done
locally for each mesh cell for each discrete directional fluxes in the
quadrature.\\
The cross section used here are the Fokker-Planck cross sections :
\begin{equation}
\Sigma_{s,l}=\frac{\alpha}{2} (L(L+1)-l(l+1))\ \ l=0,\hdots,L
\end{equation}
where $\alpha$ is the restricted momentum transfer \cite{morel_96}.
These cross sections approximate the electron scattering cross sections
\cite{morel_81} and require Galerkin quadratures , i.e.,
$D=M^{-1}$ \cite{graal}, to obtain accurate results.
\subsection{Solution techniques}
Equation (\ref{operator}) can be solved using the Source Iteration method or a
Krylov method. The Source Iteration method at the $k^{th}$ iteration is given
by :
\begin{equation}
\bs{\Phi}^{(k+1)} = DL^{-1}M\Sigma \bs{\Phi}^{(k)} + DL^{-1}\bs{Q}
\end{equation}
The spectral radius of SI can become arbitrary close to one when the
scattering ratio $\(\frac{\Sigma_{s,0}}{\Sigma_t}\)$ is close to one. 
To accelerate the convergence of SI, the Diffusion Synthetic
Acceleration scheme \cite{adams} is commonly used. The SI+DSA scheme is given by :
\begin{align}
&\bs{\Phi}^{(k+1/2)} = DL^{-1}M\Sigma\bs{\Phi}^{(k)} + DL^{-1}\bs{Q}\\
&\delta\bs{\Phi}^{(k)} = \mathcal{T}_0^{-1} R_{n\rightarrow 0} 
\(\bs{\Phi}^{(k+1/2)}-\bs{\Phi}^{(k)}\)\\
&\bs{\Phi}^{(k+1)} = \bs{\Phi}^{(k+1/2)} + P_{0/1 \rightarrow n} \delta
\bs{\Phi}^{(k)}
\end{align}
Finally, we get :
\begin{equation}
\bs{\Phi}^{(k+1)} = \((I+P_{0/1\rightarrow n} \mathcal{T}_0^{-1} R_{n\rightarrow 0} )
DL^{-1}M\Sigma-P_{0/1\rightarrow n}\mathcal{T}_0^{-1} R_{n\rightarrow 0}\)
\bs{\Phi}^{(k)} + (I+P_{0/1\rightarrow n}\mathcal{T}_0^{-1}
R_{n\rightarrow 0})DL^{-1} Q
\end{equation}
where $\mathcal{T}_0$ is the DSA operator, $R_{n\rightarrow 0}$ is the
restriction matrix of $\bs{\Phi}_{n}$ to $\bs{\Phi}_0$ and $P_{0/1 \rightarrow
n}$ is the projection matrix of $\bs{\Phi}_0$ or $\bs{\Phi}_1$, depending
whether only the zeroth or the zeroth and the first moment are accelerated, to
$\bs{\Phi}_n$.\\
When using a Krylov solver, equation (\ref{operator}) has to be rewritten as :
\begin{equation}
(I-DL^{-1}M\Sigma) \bs{\Phi} = DL^{-1}\bs{Q}
\label{krylov}
\end{equation}
where $I$ is the identity matrix. Equation (\ref{krylov}) is equation
(\ref{operator}) preconditioned by $DL^{-1}$ (sweep preconditioning). DSA can also 
help to speed up the convergence of the Krylov solver. The system of equations 
solved with the Krylov method is :
\begin{equation}
\((I+P_{0/1 \rightarrow n}\mathcal{T}_0^{-1} R_{n\rightarrow 0})(I-DL^{-1}M\Sigma)\)
\bs{\Phi} = (I+P_{0/1 \rightarrow n}\mathcal{T}_0^{-1} R_{n\rightarrow 0})DL^{-1}Q
\end{equation}       
\subsection{Review of previous angular multigrid work}
\subsubsection{One dimensional geometry}
As mentioned previously, only the zeroth and the first flux moments can be
accelerated with DSA. To accelerate higher moments, other methods have to be
used. Morel and Manteuffel have proposed an angular 
multigrid method to accelerate the inner SI calculation of the one dimension 
$S_n$ equations when the scattering is highly anisotropic 
\cite{multigrid_1d}. The motivation to use a variation of the extended
transport correction \cite{lathrop} to attenuate the ``upper half'' of the
flux moments (higher frequencies) thanks to transport sweeps. The ``lower half'' 
of the flux moments (lower frequencies) is accelerated using the $S_{n/2}$ 
equations. These $S_{n/2}$ equations are themselves 
accelerated using $S_{n/4}$ equations. The order of the transport operator is 
divided by two 
until the $S_4$ equations are solved. At this point, the $P_1$ equations are 
used to accelerate the $S_4$ equations. We define :
\begin{equation}
Half(n) = \left\{
\begin{aligned}
&\frac{n}{2}, &\textrm{if $\frac{n}{2}$ is even}\\
&\frac{n}{2}+1, &\textrm{if $\frac{n}{2}$ is odd}
\end{aligned}
\right.
\end{equation}
Their scheme works as follows : 
\begin{enumerate}
\item Perform a transport sweep for the $S_n$ equations.
\item Perform a transport sweep for the $S_{n_2}$ equations with a $P_{n_2-1}$
expansions using the $S_n$ residual as the inhomogeneous source, where
$n_2=Half(n)$.
\item Continue coarsening the angular grid by a factor two (i.e., according to
the definition of ``$Half$'') until a sweep has been performed for the $S_4$
equations.
\item Solve the $P_1$ equations (P1SA) with a $P_1$ expansion of the $S_4$
residual as the inhomogeneous source.
\item Add the Legendre moments of the diffusion solution to the Legendre
moments of the $S_4$ iterate to obtain the accelerated $S_4$ iterate.
\item Continue to add the corrections from each coarse grid to the finer grid
above to obtain the accelerated $S_n$ moments.
\end{enumerate}
Every time a transport sweep is performed, the optimal transport correction
needs to be used \cite{multigrid_1d}. For a $P_{n-1}$ expansion of the cross
sections, the corrected cross sections are given by :
\begin{equation}
\Sigma_{j}^* = \Sigma_{j} -\frac{\Sigma_{s,n/2}+\Sigma_{s,n-1}}{2}\ 
\textrm{ with }j=t \textrm{ or }s,l
\end{equation}
This correction is said to be optimal because for an infinite homogeneous medium, 
it minimizes the ``high-frequency'' angular errors, the smoothing factor being 
given by :
\begin{equation}
\rho_s =
\max(|\Sigma_{s,n/2}|/\Sigma_{s,0},|\Sigma_{s,n/2+1}|/\Sigma_{s,0},\hdots,
|\Sigma_{s,n-1}|/\Sigma_{s,0})
\end{equation}
To compare the effectiveness of the angular multigrid method with DSA, 
Fokker-Planck scattering cross sections can be used. In one dimension,
DSA becomes less efficient as $\Sigma_{s,l}$ $(l>0)$ becomes closer to
$\Sigma_{s,0}$. Therefore, in the limit as $L\rightarrow \infty$, DSA no
longer accelerates the convergence of SI when Fokker-Planck cross section are used. 
The spectral radius tends to 1.0 and thus,
the acceleration scheme is inefficient. However, the spectral radius of the
angular multigrid method has an upper bound of 0.6 when $L$ goes to
infinity.
\subsubsection{Extension to multidimensional geometries}
In the multidimensional case, DSA becomes unstable when both the zeroth
and the first flux moments are accelerated and $\frac{\Sigma_{s,1}}{\Sigma_t}
\geq 0.5$ \cite{multisweep}. In \cite{multigrid_2d}, the authors modified the
one dimensional angular multigrid method by accelerating only the zeroth flux
moment with the DSA and by using $S_2$ as lowest transport sweep
instead of an $S_4$. Moreover, a
filter is now needed to stabilize the method. Therefore, the angular multigrid 
method was modified as follows \cite{multigrid_2d} :
\begin{enumerate}
\item Perform a transport sweep for the $S_n$ equations.
\item Perform a transport sweep for the $S_{n_2}$ equations with a $P_{n_2}$
for 2-D problem and a $P_{n_2+1}$ for 3-D problem expansion for the $S_n$
residual as the inhomogeneous source, where $n_2=Half(n)$.
\item Continue coarsening the angular grid by a factor two (i.e., according to the
definition of ``$Half$'') until a sweep has been performed for the $S_2$
equations.
\item Solve the diffusion equation with a $P_0$ expansion for the $S_2$
residual as the inhomogeneous source. 
\item Apply a diffusive filter to the corrections from steps 2 and 3 (without
this filter, the method is unstable).
\item Add the corrections from steps 4 and 5 to the Legendre moments of the
$S_n$ iterate to obtain the accelerated $S_n$ moments.
\end{enumerate}
The filter stabilizes the method which otherwise would diverge but it reduces
the efficiency of the angular multigrid. The spectral radius can become
arbitrary close to one when $L$ becomes large \cite{multigrid_2d}.
\section{Angular multigrid with Krylov solver}
In this paper, we propose to abandon SI as the solver for the $S_n$ equations 
and to use the angular multigrid method as a preconditioner for the Krylov solver. 
The successive corrections of the angular multigrid acceleration form
now different stages of a preconditioner used int the Krylov solver. Since, a Krylov solver is used to
stabilize the method, two variations are possible :
\begin{itemize}
\item the coarsest level can be DSA (ANMG-DSA).
\item the coarsest level can be P1SA (ANMG-P1SA).
\end{itemize}
First, we present the angular multigrid using DSA and then, the angular
multigrid using P1SA. Later, these two versions are be compared.
\subsubsection{ANMG-DSA}
Using a method similar to the one we used to write the equation for the 
preconditioned Krylov solver, we obtain \hbox{successively :}
\begin{align}
& \Phi_n^{(k+1/2)} = D_n L_n^{-1} M_n \Sigma_n \Phi_n^{(k)} + D_n L_n^{-1} Q\\
& \delta \Phi_{n/2}^{(k)} = D_{n/2} L_{n/2}^{-1} M_{n/2} \Sigma_{n/2}
R_{n\rightarrow n/2} \(\Phi_n^{(k+1/2)}-\Phi_n^{(k)}\)\\
& \hdots\\
& \delta \Phi_2^{(k)} = D_2 L_2^{-1} M_2 \Sigma_2 R_{4\rightarrow 2} \delta \Phi_4\\
& \delta \Phi_0^{(k)} = \mathcal{T}_0^{-1} R_{2\rightarrow 0} \delta \Phi_2^{(k)} \\
& \Phi_n^{(k+1)} = \Phi_n^{(k+1/2)} + P_{n/2 \rightarrow n} \delta
\Phi_{n/2}^{(k)} + \hdots + P_{2 \rightarrow n} \delta \Phi_{2}^{(k)} + P_{0
\rightarrow n} \delta \Phi_{0}^{(k)}
\end{align}

\begin{equation}
\begin{split}
\Phi_n^{(k+1)} =& T_n \Phi_n^{(k)} + D_n L_n^{-1} Q +
P_{n/2 \rightarrow n} \(T_{n/2}
R_{n\rightarrow n/2} \(\Phi_n^{(k+1/2)} - \Phi_n^{(k)}\)\)+\hdots \\
&+ P_{2 \rightarrow n} T_2 R_{4\rightarrow 2} \delta
\Phi_{4}^{(k)} + P_{0\rightarrow n} \mathcal{T}_0^{-1} R_{2\rightarrow 0} \delta 
\Phi_2^{(k)}\\
=& T_n \Phi_n^{(k)} + D_n L_n^{-1} Q + P_{n/2 \rightarrow
n} \(T_{n/2} R_{n \rightarrow n/2}\(T_n \Phi_n^{(k)} +D_n L_n^{-1} Q -\Phi_n^{(k)}
\)\)\\
& +\hdots + P_{2\rightarrow n} T_2 R_{4\rightarrow 2} 
\(T_4 R_{8\rightarrow 4}\( \hdots \(T_n \Phi_n^{(k)} + D_n L_n^{-1} Q -
 \Phi_n^{(k)}\)\) \) \\ 
&+ P_{0\rightarrow n} \mathcal{T}_0^{-1} R_{2\rightarrow 0}\(T_2 R_{4\rightarrow 2} 
\(\hdots\(T_n \Phi_n^{(k)}+D_n L_n^{-1}Q-\Phi_n^{(k)}\)\)\)\\
=& \(T_n + P_{n/2\rightarrow n} T_{n/2} R_{n\rightarrow n/2}\(T_n-I\)+
 \hdots + P_{2\rightarrow n} T_2 R_{4\rightarrow}
\(T_4 R_{8\rightarrow 4} \(\hdots\(T_n -I\)\)\)\right.\\ 
&\left. +P_{0\rightarrow n} \mathcal{T}_0^{-1} R_{2\rightarrow 0}  \(T_2
R_{4\rightarrow 2} (\hdots \(T_n-I\))\)\) \Phi_n^{(k)}
+\(I+P_{n/2\rightarrow n} T_{n/2} R_{n\rightarrow
n/2}+ \hdots + \right.\\
&\left. P_{2\rightarrow n} T_2 R_{4\rightarrow 2} \(T_4
 R_{8\rightarrow 4}\(\hdots
\(T_{n/2}R_{n\rightarrow n/2}\)\)\)+\right.\\
& \left. P_{0\rightarrow n} \mathcal{T}_0^{-1}R_{2\rightarrow 0}
\(T_2 R_{4\rightarrow 2}\(\hdots\(T_{n/2}R_{n\rightarrow n/2}\)\)\)\)
D_nL_n^{-1} Q
\end{split}
\end{equation}
where $T_n = D_n L_n^{-1}M_n \Sigma_n$. We use the subscript $n$ as a reminder
that we are solving the $S_n$ equations.\\
Finally, the system of equations which has to be solved is :
\begin{equation}
\begin{split}
&(I+P_{{n}/{2}\rightarrow n }
T_{{n}/{2}} (I+P_{{n}/{4}\rightarrow {n}/{2}}T_{{n}/{4}} (\hdots
(I+P_{0\rightarrow 2} \mathcal{T}_0^{-1} R_{2\rightarrow 0})\hdots)
R_{{n}/{2}\rightarrow {n}/{4}})R_{n\rightarrow{n}/{2}})(I-T_n)
\bs{\Phi}_n =\\
& (I+P_{{n}/{2}\rightarrow n} T_{{n}/{2}} (I+P_{{n}/{4}
\rightarrow {n}/{2}} T_{{n}/{4}} (\hdots (I+P_{0 \rightarrow
2}\mathcal{T}_0^{-1} R_{2\rightarrow 0})\hdots)R_{{n}/{2}\rightarrow
{n}/{4}})R_{n\rightarrow {n}/{2}} ) D_n L_n^{-1} Q
\end{split}
\label{anmg-dsa}
\end{equation}  
At this point, it is necessary to choose a DSA scheme. Among different
schemes (see \cite{adams}), the Modified Interior Penalty (MIP) DSA was
chosen \cite{mip}. This DSA is based on a second-order discontinuous of a
diffusion equation, as opposed to a mixed of $P1$ formulation.
It uses bilinear discontinuous finite elements, which is
the same spatial discretization that the one chosen for the
$S_n$ equations and it has been shown to be always stable for isotropic
scattering and is symmetric positive definite (SPD), which makes it easy to invert.
We will recall here the weak form of this DSA :
\begin{equation}
b_{MIP}(\phi,\phi^*) = l_{MIP}(\phi^*)
\end{equation}
with :
\begin{equation}
\begin{split}
b_{MIP}(\phi,\phi^*) =& (\Sigma_a \phi,\phi^*)_{\partial D} +
\(\mathrm{D}\bn\phi,\bn\phi^*\)_{\mathcal{D}} + \(\kappa_e\llb\phi\rrb,
\llb\phi^*\rrb\)_{E_h^i}
+ \(\llb\phi\rrb,\ldb \mathrm{D}\partial_n \phi^*\rdb\)_{E_h^i} +\\
&(\ldb \mathrm{D} \partial_n \phi\rdb,\llb\phi^*\rrb)_{E_h^i} + 
(\kappa_e\phi,\phi^*)_{\partial
D^d}-\frac{1}{2} \(\phi,\mathrm{D}\partial_n \phi^*\)_{\partial
\mathcal{D}^d} - \frac{1}{2} (\mathrm{D} \partial_n \phi,\phi^*)_{\partial 
\mathcal{D}^d}
\end{split}
\end{equation}
\begin{equation}
l_{MIP}(\phi^*) = (Q_0,\phi^*)_{\mathcal{D}} 
\end{equation}
where :
\begin{itemize}
\item $(f,g)_{\mathcal{D}} = \sum_{K\in \mathbb{T}_h} \int_K fg\ d\br$ and 
$(f,g)_{E_h^i} = \sum_{e\in E_h^i} \int_e fg\ ds$
\item $\mathbb{T}_h$ is the mesh used to discretize the domain $\mathcal{D}$
into nonoverlapping elements $K$, $E_h^i$ is the set of interior edges,
$\mathcal{D}$ is the spatial domain, $\partial \mathcal{D}^d$ is the boundary
of the domain with Dirichlet condition and $\partial \mathcal{D}^r$ is the
boundary of the domain with reflective condition
\item $\Sigma_a$ is the absorption macroscopic cross section
\item $\mathrm{D}$ is the diffusion coefficient
\item $\partial_n = \bs{n}\cdot \bn$ where $\bs{n}$ is the outward unit
normal
\item $\llb \phi\rrb = \phi^{+}-\phi^{-}$ is the jump of at the interface
between two elements
\item $\ldb\phi\rdb = \frac{\phi^++\phi^-}{2}$ is the mean of $\phi$ at the
interface between two elements
\item $\phi^{\pm}(\br)=\lim_{s\to 0^{\pm}}\phi(\br+s\bs{n}_e)$, $\bs{n}_e$ is
the normal unit vector associated with a given edge $e$
\item $\kappa_e = \max\(\kappa_e^{IP},\frac{1}{4}\)$ with
$\kappa_e^{IP}=\left\{
\begin{aligned}
&\frac{c(p^+)}{2}\frac{D^+}{h_{\bot}^+} + \frac{c(p^-)}{2}
\frac{D^-}{h_{\bot}^-} &\textrm{ on interior edges, i.e. }e\in E_h^i\\
&c(p)\frac{D}{h_{\bot}} & \textrm{ on boundary edges,
i.e. }e\in\partial\mathcal{D}^d
\end{aligned}
\right.$\\
$c(p)$ is given by $c(p)=2p(p+1)$, $p$ is the polynomial order and $h_{\bot}$
is the length of the cell in the direction orthogonal to the edge $e$
\end{itemize}

\subsubsection{ANMG-P1SA}
Using P1SA and $S_4$ as the lowest $S_n$ order instead of DSA and $S_2$ in 
equation (\ref{anmg-dsa}) gives us :
\begin{equation}
\begin{split}
& (I+P_{n/2\rightarrow n} T_{n/2} (I+P_{n/4\rightarrow n/2}
T_{n/4}(\hdots(I+P_{1\rightarrow 4}\mathcal{T}_1^{-1} R_{4\rightarrow
1})\hdots)R_{n/2 \rightarrow n/4})R_{n\rightarrow n/2}) (I-T_n)\bs{\Phi}_n = \\
& (I+P_{n/2\rightarrow n} T_{n/2} (I+P_{n/4\rightarrow n/2}
T_{n/4}(\hdots(I+P_{1\rightarrow 4}\mathcal{T}_1^{-1} R_{4\rightarrow
1})\hdots)R_{n/2\rightarrow n/4})R_{n\rightarrow n/2}) D_n L_n^{-1} Q
\end{split}
\end{equation}
where $\mathcal{T}_1$ is the P1SA operator.\\
The P1SA used is the P1C defined in \cite{yaqi}. This scheme,
which is positive definite but non-symmetric, is given by :
\begin{equation}
b_{P1C}(\Phi,\bs{J},\Phi^*,\bs{J}^*) = l_{P1C}(\Phi^*,\bs{J}^*)
\end{equation}
with :
\begin{equation}
\begin{split}
b_{P1}(\Phi,\bs{J},\Phi^*,\bs{J}^*) = & (\Sigma_a \Phi,\Phi^*)_{\mathcal{D}} +
(3\Sigma_{tr} \bs{J},\bs{J}^*)_{\mathcal{D}} + (\bn
\Phi,\bs{J}^*)_{\mathcal{D}} - (\bs{J},\bn \Phi^*)_{\mathcal{D}}\\
&+\frac{1}{4} \(\llb\Phi\rrb,\llb\Phi^*\rrb\)_{E_h^i} +
\(\llb\Phi\rrb,\ldb\bs{J}\cdot\bs{n}_e\rdb\)_{E_h^i} - (\ldb
\bs{J}\cdot\bs{n}_e\rdb, \llb\Phi^*\rrb)_{E_h^i}\\
&+\frac{9}{16}\(\llb\bs{J}\cdot\bs{n}_e\rrb,\llb\bs{J}^*\cdot\bs{n}_e\rrb\)_{E_h^i}
+ \frac{9}{16}\(\llb\bs{J}\rrb,\llb\bs{J}^*\rrb\)_{E_h^i}\\
&+\frac{1}{4}(\Phi,\Phi^*)_{\partial \mathcal{D}^d} +
\frac{1}{2}(\Phi,\bs{J}^*\cdot\bs{n}_e)_{\partial \mathcal{D}^d} - \frac{1}{2}
(\bs{J}\cdot\bs{n}_e,\Phi^*)_{\partial\mathcal{D}^d}\\
&+\frac{9}{16}(\bs{J},\bs{J}^*)_{\partial
\mathcal{D}^d}+\frac{9}{16}(\bs{J}\cdot\bs{n}_e,\bs{J}^*\cdot\bs{n}_e)_{\partial 
\mathcal{D}^d} + \frac{9}{4} (\bs{J}\cdot\bs{n}_e,\bs{J}^*\cdot\bs{n}_e)_{\partial
\mathcal{D}^r}
\end{split}
\end{equation}
\begin{equation}
l(\Phi^*,\bs{J}^*) = (Q_0,\Phi^*)_{\mathcal{D}} +
(3\bs{Q}_1,\bs{J}^*)_{\mathcal{D}}
\end{equation}
where $\bs{J}$ is the current or first moment of the flux and 
$\Sigma_{tr}=\Sigma_t-\Sigma_{s,1}$.
